---
title: "Average Age of Members of Congress"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load all packages here
library(ggplot2)
library(dplyr)
library(fivethirtyeight)
# For reading CSV spreadsheet files:
library(readr)
```

## Introduction

Analyzing the age of members of the United States congress over the years. The data of interest is saved in the `congress_age` data frame included in the `fivethirtyeight` package. To understand the data's context, first read:

* The original FiveThirtyEight [article](https://fivethirtyeight.com/features/both-republicans-and-democrats-have-an-age-problem/) the data was used in. In particular the first visualization titled "Average Age of Members of Congress"

## Data Wrangling


```{r }
avg_congress_age<- congress_age %>% 
  group_by(termstart,party) %>% 
  filter(party=="D"|party=="R") %>% 
  summarize(mean_age=mean(age)) %>% 
  select(party,termstart,mean_age)
avg_congress_age
```

## Data Visualization

```{r pressure, echo=FALSE}
ggplot(data=avg_congress_age, mapping=aes(x=termstart, y=mean_age,color=party))+
  labs(x="Date", title="Average Age of Members of Congress", subtitle = "At start of term, 1947-2013")+
  geom_line()+
  scale_y_continuous(name="Average age", limits = c(40,61))+
  scale_color_manual(values=c("Blue","Red"))
  
```

